Reproducible Research - Project 1
=================================

## 1. Mean and Total Steps

### Load Data
```{r loaddata}
fit <- read.csv("activity.csv")
```

### Omit NA & Aggregate number of steps per day
```{r omitna}
fit2 <- na.omit(fit)
fit3 <- aggregate(fit2$steps,fit2[2],sum)
```

### Draw a histr plot for number of steps in a day
```{r drawhist,echo=TRUE}
hist(fit3$x,col="green",main="Historgram of Number of Steps per day",xlab="Number of Steps",ylab="Count of Days")
```

### Computing Mean steps
```{r mean,echo = TRUE}
mean(fit3$x)
```

### Computing Median steps
```{r median,echo=TRUE}
median(fit3$x)
```
## 2. Average Daily Activity Pattern

### Creating 5 min plot intervals

Find average across intervals

```{r interval,echo=TRUE}
fit4 <- aggregate(fit2$steps,fit2[3],mean)
```

Draw Plot
```{r intplot,echo=TRUE}
plot(x~interval,data=fit4,type='l',col="red",xlab="At Interval",ylab="Mean steps per day",main="Average Daily Activity Pattern")
```

### Peak Interval
```{r peakint,echo=TRUE}
fit4[which(fit4$x==max(fit4$x)),1]
```

## 3. Imputing Missing Values

### Count Missing Values
```{r missing,echo=TRUE}
 missing <- nrow(fit[(!complete.cases(fit)),])
```
The number of rows with missing data are `r missing`.

### Fill in Missing Values

```{r impute,echo=TRUE}
fit5 <- aggregate(fit2$steps,fit2[3],mean)
fit6 <- merge(x=fit,y=fit5,by="interval",all.x=TRUE)
fit6$steps <- ifelse(is.na(fit6$steps),fit6$x,fit6$steps)
fit7 <- fit6[,-c(4)]
```

### Draw 2nd Hist of Steps per Day

```{r drawhist2,echo=TRUE}
  fit8 <- aggregate(fit7$steps,fit7[3],sum)
  hist(fit8$x,col="green",main="2nd Historgram of Number of Steps per day",xlab="Number of Steps",ylab="Count of Days")
```

### Computing 2nd Mean
```{r mean2,echo = TRUE}
mean(fit8$x)
```

### Computing 2nd Median
```{r median2,echo=TRUE}
median(fit8$x)
```

## 4. Activity Pattern: Weekdays vs Weekends

Factoring Weekday and Weekend from Date

```{r wkday,echo=TRUE}
fit9 <- fit7
fit9$date1 <- as.Date(fit9$date,format="%Y-%m-%d")
fit9$flag1 <- weekdays(fit9$date1)
fit9$flag2 <- fit9$flag1=="Sunday" | fit9$flag1=="Saturday"
fit9$flag3 <- factor(ifelse(fit9$flag2,"weekend","weekday")) 
```

Plot to compare activity by Weekday/Weekend
```{r wkplot,echo=TRUE}
fit10<- aggregate(fit9$steps,fit9[c(1,7)],mean)
library(lattice)
xyplot(x ~ interval | flag3,data=fit10,layout=c(1,2),type="l",xlab="Interval",ylab="Number of steps")
```
